Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-08 paper/paper.tex
quick pass on abstract and intro

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,review, anonymous]{acmart}
\acmConference[ISSTA 2020]{ACM SIGSOFT International Symposium on Software Testing and Analysis}{18–22 July, 2020}{Los Angeles, US}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Network Intrusion Detection Systems (\nids{}) are a popular mechanism
used by system administrators to defend against network attacks. These
systems monitor the network traffic and flag suspicious network
behavior. Signature-based \nids\ do that by checking the network
traffic against a pre-defined set of rules, which can become obsolete
as attackers learn new strategies to circumvent existing defenses.
This paper proposes \tname{}, a technique that automatically
synthesizes \nids\ rules from positive and negative examples, \ie{},
malicious and benign traffic. \tname{} formulates synthesis as an
optimization problem whose candidate solutions are rules that maximize
the capture of positive traffic and minimize the capture of negative
traffic. \tname{} bootstraps the search with candidate solutions that
use data from the payload of the malicious message and produces
optimal rule candidates on output. We evaluated \tname{} on a diverse
set of attacks. Results indicate that \Fix{...}
\end{abstract}

>>>>

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
\documentclass[sigconf,review, anonymous]{acmart}
\acmConference[ESEC/FSE 2020]{The 28th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{8 - 13 November, 2020}{Sacramento, California, United States}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Network Intrusion Detection Systems (\nids{}) are a popular mechanism
used by system administrators to defend against network attacks. These
systems monitor the network traffic and flag suspicious network
behavior. Signature-based \nids\ do that by checking the\MyComment{ network}
traffic against a pre-defined set of rules, which become obsolete
as attackers learn new strategies to circumvent existing defenses.

This paper proposes \tname{}, a technique that automatically
synthesizes \nids\ rules from positive and negative examples, \ie{},
malicious and benign traffic. \tname{} formulates synthesis as an
optimization problem whose candidate solutions are rules. Optimal
solutions maximize the capture of positive traffic and minimize the
capture of negative traffic. \tname{} bootstraps the search with a
candidate solution inferred from the payload of the malicious message.
It uses that initial overfitting solution to search for alternative
rules that only capture the malicious traffic. Then, it ranks those
rules according to heuristics---drawn from a data set of existing
rules---denoting the likelihood of those rules of being useful.

We evaluated \tname{} on a diverse
set of attacks. Results indicate that \Fix{...}
\end{abstract}
